---
output:
    pdf_document
always_allow_html: yes
---
---
title: `r submitter`
date: `r gsub(" 0", " ", format(start_date, format="%B %d, %Y"))` - `r gsub(" 0", " ", format(end_date, format="%B %d, %Y"))`
---
\pagenumbering{gobble}
 
```{r, echo=FALSE, message=FALSE}
message <- messages[messages$Hospital == submitter, 2]
```
 
```{r, echo=FALSE, message=FALSE}
h <- hospital_metrics[hospital_metrics$SUBMITTERNAME==submitter,]
hospital_filt <- ungroup(hospital_metrics_plot)
h_plot <- hospital_filt[hospital_filt$SUBMITTERNAME==submitter,]
h_plot$SUBMITTERNAME <- 'Hospital'
max_unsat_h <- max(max_overall_unsat, h_plot$unsat_percent)
min_transit_h <- min(min_transit_percent, h_plot$percent_rec_in_2_days)
bound <- rbind(h_plot, state_plot)
title1 = "Percentage of Samples Received\nwithin Two Days of Collection"
title2 = " Percentage of Unsatisfactory Samples\nReceived (Requiring Repeat Collection)"
```
 
|      | Hospital || Hospital Rank | Virginia |
| -------------------------------------|--------|--------|---------|---------|
| **Number of samples submitted** | `r format(h$total_samples, big.mark=",", trim=TRUE)` |  |  | `r format(state$total_samples, big.mark=",", trim=TRUE)` |
| **Average transit time** | `r h$avg_transit_time` days |  | `r toOrdinal(h$rank_transit)` of `r state$submitters` | `r state$avg_transit_time` days |
| **Samples received within 2 days of** |  |  |  |  | 
| **&nbsp;&nbsp;&nbsp;&nbsp;collection (GOAL: 95%)** | `r format(h$rec_in_2_days, big.mark=",", trim=TRUE)` | `r h$percent_rec_in_2_days`% | `r toOrdinal(h$rank_percent_within_goal)` of `r state$submitters` | `r state$percent_rec_in_2_days`% |
| **Samples collected at < 24 hours of age** | `r h$col_less_than_24_hours` | `r h$percent_less_than_24_hours`% | `r toOrdinal(h$rank_early_collection)` of `r state$submitters` | `r state$percent_less_than_24_hours`%
| **Samples transfused prior to collection** |  `r h$trans` | `r h$trans_percent`% |  `r toOrdinal(h$rank_transfused)` of `r state$submitters`  |  `r state$trans_percent`% |
| **Unsatisfactory samples** | `r h$unsat_count` |  `r h$unsat_percent`% | `r toOrdinal(h$rank_unsats)` of `r state$submitters`  | `r state$unsat_percent`% |
 
```{r, echo=FALSE, results='markdown', message=FALSE}
# create table of unsat counts for hospital
temp_unsats <- as.data.frame(t(select(h, eval(as.name(as.character(unsats$description[1]))):eval(as.name(as.character(unsats$description[nrow(unsats)]))))))
temp_unsats$Type <- row.names(temp_unsats)
temp_unsats <- temp_unsats[,c(2,1)]
names(temp_unsats) <- c('Type','Count')
 
# remove all rows with NA for counts
unsats_final <- temp_unsats[!is.na(temp_unsats$Count),]
 
# show unsat counts for each category if unsats_final has more than 0 observations
if (nrow(unsats_final) > 0) {
  kable(unsats_final, row.names=FALSE, col.names=c('Unsatisfactory Samples','Count'))
}
```
 
&nbsp;&nbsp;  
 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
 
if (line_chart == 'quarterly') {
  
  # Plot percentage of samples received within 2 days over past 4 quarters
  p1 <- ggplot(bound, aes(x=PERIOD, y=percent_rec_in_2_days, colour=SUBMITTERNAME, group=rev(SUBMITTERNAME))) +
    scale_x_yearqtr(breaks = seq(from = min(bound$PERIOD), to = max(bound$PERIOD), by = 0.25), format = "%Y Q%q") +
    scale_y_continuous(limits=c(min_transit_h, 100)) +
    labs(x="Quarter", y="Percentage") +
    ggtitle(bquote(.(title1))) + 
    geom_line(size=2) +
    geom_point(data=bound[bound$SUBMITTERNAME == 'Hospital',]) +
    geom_hline(color="green4", aes(yintercept=95), size=1) +
    geom_text(color="green4", size=3, aes(x=(as.numeric(min(bound$PERIOD)) + .2), 
                                          y=93, label="Goal: 95% of samples", vjust=1)) + 
    scale_color_manual(values=c("blue","grey59")) +
    theme(legend.title=element_blank()) + 
    theme(legend.position="bottom") +
    theme(legend.text = element_text(size = 10)) +
    theme(plot.title = element_text(size = 10, face = "plain")) +
    theme(plot.margin = unit(c(0.6,0.5,0.3,0.3), "cm"))
  
  # Plot percentage of unsatisfactory samples over past 4 quarters
  p2 <- ggplot(bound, aes(x=PERIOD, y=unsat_percent, colour=SUBMITTERNAME, 
                  group=rev(SUBMITTERNAME))) +
    scale_x_yearqtr(breaks = seq(from = min(bound$PERIOD), to = max(bound$PERIOD), by = 0.25),
                  format = "%Y Q%q") +
    scale_y_continuous(limits=c(0, max_unsat_h)) +
    labs(x="Quarter", y="Percentage") +
    ggtitle(bquote(.(title2))) + 
    geom_line(size=2) +
    geom_point(data=bound[bound$SUBMITTERNAME == 'Hospital',]) +
    scale_color_manual(values=c("blue","grey59")) +
    theme(legend.title=element_blank()) +
    theme(legend.position="bottom") +
    theme(legend.text = element_text(size = 10)) +
    theme(plot.title = element_text(size = 10, face = "plain")) +
    theme(plot.margin = unit(c(0.6,0.3,0.3,0.5), "cm"))
  
} else {
  
   # Plot percentage of samples received within 2 days over past 12 months
   p1 <- ggplot(bound, aes(x=PERIOD, y=percent_rec_in_2_days, colour=SUBMITTERNAME, group=rev(SUBMITTERNAME))) +
    scale_x_yearmon(breaks = seq(from = min(bound$PERIOD), to = max(bound$PERIOD), by = 0.25),
                  format = "%b %Y") +
    scale_y_continuous(limits=c(min_transit_h, 100)) +
    labs(x="Month", y="Percentage") +
    ggtitle(bquote(.(title1))) + 
    geom_line(size=2) +
    geom_point(data=bound[bound$SUBMITTERNAME == 'Hospital',]) +
    scale_color_manual(values=c("blue","grey59")) +
    geom_hline(color="green4", aes(yintercept=95), size=1) +
    geom_text(color="green4", size=3, aes(x=(as.numeric(min(bound$PERIOD)) + .25), y=93, label="Goal: 95% of samples", vjust=1)) + 
    theme(legend.title=element_blank()) + 
    theme(legend.position="bottom") +
    theme(legend.text = element_text(size = 10)) +
    theme(plot.title = element_text(size = 10, face = "plain")) +
    theme(plot.margin = unit(c(0.6,0.5,0.3,0.3), "cm"))
 
# Plot percentage of unsatisfactory samples over past 12 months
  p2 <- ggplot(bound, aes(x=PERIOD, y=unsat_percent, colour=SUBMITTERNAME, 
                  group=rev(SUBMITTERNAME))) +
    scale_x_yearmon(breaks = seq(from = min(bound$PERIOD), to = max(bound$PERIOD), by = 0.25),
                  format = "%b %Y") +
    scale_y_continuous(limits=c(0, max_unsat_h)) +
    labs(x="Month", y="Percentage") +
    ggtitle(bquote(.(title2))) + 
    geom_line(size=2) +
    geom_point(data=bound[bound$SUBMITTERNAME == 'Hospital',]) +
    scale_color_manual(values=c("blue","grey59")) +
    theme(legend.title=element_blank()) +
    theme(legend.position="bottom") +
    theme(legend.text = element_text(size = 10)) +
    theme(plot.title = element_text(size = 10, face = "plain")) +
    theme(plot.margin = unit(c(0.6,0.3,0.3,0.5), "cm"))
}
 
pushViewport(viewport(layout = grid.layout(1, 2)))
print(p1, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(p2, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
 
```
 
\begin{center}
`r if(!identical(message,character(0))) {message}`
\end{center}
