---
output:
  pdfdocument:
    latexengine: xelatex
always_allow_html: yes
---
---
title: `r submitter`
---
 
```{r, include=FALSE, cache=FALSE, echo=FALSE}
library(knitr)
library(markdown)
library(rmarkdown)
```
 
 
```{r, echo=FALSE}
h <- hospital_metrics[hospital_metrics$SUBMITTERNAME==submitter,]
hospital_filt <- ungroup(hospital_metrics_plot)
h_plot <- hospital_filt[hospital_filt$SUBMITTERNAME==submitter,]
h_plot$SUBMITTERNAME <- 'Hospital'
max_unsat_h <- max(max_overall_unsat, h_plot$unsat_percent)
max_transit_h <- max(max_overall_transit, h_plot$avg_transit_time)
bound <- rbind(h_plot, state_plot)
```
 
 
|      | Hospital || Hospital Rank | Virginia |
| -------------------------------------|--------|--------|---------|---------|
| **Number of samples submitted** | `r format(h$total_samples, big.mark=",", trim=TRUE)` |  |  | `r format(state$total_samples, big.mark=",", trim=TRUE)` |
| **Average transit time** | `r round(h$avg_transit_time, digits=2)` days |  | `r h$rank_transit` of `r state$submitters` | `r round(state$avg_transit_time, digits=2)` days |
| &nbsp;&nbsp;&nbsp;&nbsp;Minimum transit time | `r h$min_transit_time` days |  |  |  |
| &nbsp;&nbsp;&nbsp;&nbsp;Maximum transit time | `r h$max_transit_time` days |  |  |  |
| **Samples received within 2 days (GOAL: 95%)** | `r h$rec_in_2_days` | `r round(h$percent_rec_in_2_days, digits=2)`% | `r h$rank_percent_within_goal` of `r state$submitters` | `r round(state$percent_rec_in_2_days, digits=2) * 100`% |
| &nbsp;&nbsp;&nbsp;&nbsp;Met goal? | `r ifelse(h$met_goal==1, 'No', 'Yes')`|  |  |  | 
| **Samples collected at < 24 hours of age** | `r h$col_less_than_24_hours` | `r round(h$percent_less_than_24_hours, digits=4)*100`% | `r h$rank_early_collection` of `r state$submitters` | `r round(state$percent_less_than_24_hours, digits=4)*100`%
| **Samples transfused prior to collection** |  `r h$trans` | `r round(h$trans_percent, digits=4)*100`% |  `r h$rank_early_collection` of `r state$submitters`  |  `r round(state$trans_percent, digits=4)*100`% |
| **Unsatisfactory samples** | `r h$unsat_count` |  `r round(h$unsat_percent, digits=4)*100`% | `r h$rank_unsats` of `r state$submitters`  | `r round(state$unsat_percent, digits=4)*100`% | 
 
```{r, echo=FALSE, results='markdown'}
# combine hospital's unsat counts with descriptions of codes
temp_unsats <- as.data.frame(t(select(h, unsat_1:unsat_13)))
names(temp_unsats) <- c('count')
unsats_count <- cbind(unsats, temp_unsats)
 
# remove all rows with NA for counts
unsats_final <- unsats_count[!is.na(unsats_count$count),]
 
# show unsat counts for each category if unsats_final has more than 0 observations
if (nrow(unsats_final) > 0) {
  unsats_final <- unsats_final[,2:3]
  names(unsats_final) <- c('Unsatisfactory Samples','Count')
  kable(unsats_final, row.names=FALSE)
}
```
 
```{r, fig.width=3.2, echo=FALSE}
 
# Plot average transit time over past 4 quarters
ggplot(bound, aes(x=QUARTER, y=avg_transit_time, colour=SUBMITTERNAME, group=rev(SUBMITTERNAME))) +
  scale_x_yearqtr(breaks = seq(from = min(bound$QUARTER), to = max(bound$QUARTER), by = 0.25),
                  format = "%Y Q%q") +
  scale_y_continuous(limits=c(min_overall_transit, max_transit_h)) +
  labs(x="Quarter", y="Days") +
  ggtitle(bquote(atop("Average Transit Time", atop(italic(.(submitter)), "")))) + 
  geom_line(size=2) +
  scale_color_manual(values=c("blue","grey59")) +
  geom_hline(color="green4", aes(yintercept=2), size=2) +
  geom_text(color="green4", size=3, aes(x=(as.numeric(min(bound$QUARTER)) + .18), y=min_overall_transit, label="Goal: under 2 days")) + 
  theme(legend.title=element_blank()) + 
  theme(legend.position="bottom") +
  theme(legend.text = element_text(size = 10)) +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  theme(plot.margin = unit(c(0.3,0.3,0.3,0.3), "cm"))
 
# Plot percentage of unsatisfactory samples over past 4 quarters
ggplot(bound, aes(x=QUARTER, y=unsat_percent, colour=SUBMITTERNAME, 
                  group=rev(SUBMITTERNAME))) +
  scale_x_yearqtr(breaks = seq(from = min(bound$QUARTER), to = max(bound$QUARTER), by = 0.25),
                  format = "%Y Q%q") +
  scale_y_continuous(limits=c(0, max_unsat_h)) +
  labs(x="Quarter", y="Percentage") +
  ggtitle(bquote(atop("Percentage of Unsatisfactory Samples", atop(italic(.(submitter)), "")))) +
  geom_line(size=2) +
  scale_color_manual(values=c("blue","grey59")) +
  theme(legend.title=element_blank()) +
  theme(legend.position="bottom") +
  theme(legend.text = element_text(size = 10)) +
  theme(plot.title = element_text(size = 10, face = "bold")) +
  theme(plot.margin = unit(c(0.3,0.3,0.3,0.3), "cm"))
```
