---
output:
  pdfdocument:
    latexengine: xelatex
mainfont: Arial
sansfont: Arial
always_allow_html: yes
---
---
title: `r submitter`
---

```{r, echo=FALSE}
library(knitr)
library(markdown)
library(rmarkdown)
```


```{r, echo=FALSE}
h <- hospital_metrics[hospital_metrics$SUBMITTERNAME==submitter,]
```


|                                   | Hospital | Percent | Ranking | Virginia |
| ----------------------------------|------|------|-----------|
| **Number of samples submitted** | `r h$total_samples` | -- | -- | `r state$total_samples` |
| **Average transit time** | `r h$avg_transit_time` | -- | `r h$rank_transit` of `r state$submitters` | `r state$avg_transit_time` |
| **Samples collected at < 24 hours of age** | `r h$col_less_than_24_hours` | `r h$percent_less_than_24_hours` | `r h$rank_early_collection` | `r state$percent_less_than_24_hours`
| **Samples transfused prior to collection** |                              |                                  |      |
| **Unsatisfactory samples**                 | `r h$unsat_count`            |                                  |      |




