---
output:
  pdfdocument:
    latexengine: xelatex
mainfont: Arial
sansfont: Arial
always_allow_html: yes
---
---
title: `r submitter`
---

```{r, echo=FALSE}
library(knitr)
library(markdown)
library(rmarkdown)
```


```{r, echo=FALSE}
h <- hospital_metrics[hospital_metrics$SUBMITTERNAME==submitter,]
```


Today is `r Sys.Date()`,

The number of total samples collected is `r h$total_samples`.

|                                   | Hospital || Virginia |
| ----------------------------------|------|------|-----------|
| **Number of samples submitted**            | `r h$total_samples`          | ---                              | VA 1 |
| **Average transit time**                   | `r h$avg_transit_time`       | ---                              | VA 2 |
| **Samples collected at < 24 hours of age** | `r h$col_less_than_24_hours` | `r h$percent_less_than_24_hours` | VA 3 |
| **Samples transfused prior to collection** |                              |                                  |      |
| **Unsatisfactory samples**                 | `r h$unsat_count`            |                                  |      |

                                                                                  Hospital                                       Virginia
-------------------------------------------------  ---------------------------------------------------------------------        ----------
**Number of samples submitted**                        `r h$total_samples`       ---
**Average transit time**                               `r h$avg_transit_time` &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;        --- 
**Samples collected at < 24 hours of age**             `r h$col_less_than_24_hours` &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  `r h$percent_less_than_24_hours`
**Samples transfused prior to collection**
**Unsatisfactory samples**                             `r h$unsat_count`
-------------------------------------------------   ---------------------------------------------------------------------       ----------


